### 2013-12-13 manuscripts/reply/reply-main.tex
Updating reply ms.
Incorporating changes made in `short-repy.tex` into `reply.tex` and
`reply-main.tex`. Leaving `short-reply.tex` in repo, because Mark has
been working on this copy.

Recently, the journal \emph{Evolution} has served as a medium for a discussion
of potential promises and pitfalls of approximate-Bayesian methods of
comparative phylogeographical model choice and prior selection.
The discussion has centered around the model-choice method, \msb
\citep{Huang2011}, which uses approximate Bayesian computation (ABC) to
estimate the temporal distribution of divergences among co-distributed pairs of
taxa by sampling over models of divergence that range from a single
divergence-time parameter (i.e., all pairs of taxa diverged at the same time)
to the fully generalized model in which each pair is assigned a divergence-time
parameter.
A full description of the model is given in \citet{Oaks2012}.

\citet{Oaks2012} published results of simulation-based power analyses showing
that \msb is biased toward inferring models of temporally clustered divergence
times across taxon pairs.
\citet{Hickerson2013} published a response to \citet{Oaks2012} where they
present an empirical Bayesian model-averaging approach that they conclude
circumvents the problems revealed by \citet{Oaks2012}.
These papers are largely in agreement, with \citet{Hickerson2013} reiterating
much of the discussion of \citet{Oaks2012} regarding the impact of broad
uniform priors on Bayesian model choice.
Both papers agree that when broad uniform priors are used to reflect \emph{a
prior} uncertainty about divergence times of all pairs of taxa under study,
the method can be biased toward inferring biogeographically interesting
scenarios of temporally clustered divergences among taxa (i.e. models with few
divergence-time parameters).
Both papers also agree that this bias toward models with few divergence-time
parameters is due to the much greater parameter space of models with more
divergence-time parameters.
However, the papers disgree about the primary mechanism by which the greater
parameter space of parameter-rich models causes the bias toward clustered
divergence models;
\citet{Oaks2012} suggest a statistical issue is the cause, whereas
\citep{Hickerson2013} prefer a numerical explanation.
% The main areas of disagreement between the papers are centered around
% (1) the mechanism by which broad uniform priors cause the bias of \msb toward
% models with few divergence-time parameters, and
% (2) how to potentially mitigate this issue.

\citet{Oaks2012} suggest the primary cause of the bias of \msb is the low
marginal likelihoods of parameter-rich models integrated over vast parameter
space with low probability of producing the data, yet relatively high prior
density \citep{Lindley1957} imposed by the uniformly distributed prior on
divergence times.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is intrinsic to \msb, concluding the
method's rejection algorithm is inefficient and will be biased
toward models with fewer divergence-time parameters, because the parameter
space of these models are more densely sampled relative to models with more
divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results of additional analyses that, when combined with
the results of \citet{Oaks2012}, strongly suggest small marginal likelihoods of
models with more parameter space is a primary mechanism by which uniform priors
are causing the bias of \msb.

% We show that this argument is based on empirical Bayesian reasoning and
% questionable assumptions, and does not explain the bias of the method found in
% many of the analyses of \citet{Oaks2012}.

There are also differences between the papers regarding potential solutions to
the bias.
\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times and other nuisance parameters could increase the marginal
likelihoods of models with more divergence-time parameters and thus reduce the
bias.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
% \citet{Hickerson2013} champion this strategy as a means of avoiding the
% pitfalls raised by \citet{Oaks2012}.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for an already biased model-choice method.

In this paper, we discuss the potential theoretical and practical problems of
using empirically informed priors for Bayesian model choice.
Furthermore, we evaluate the empirical Bayesian model averaging approach of
\citet{Hickerson2013} as a potential solution to the biases revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different time units, which makes the results presented
in their response difficult to interpret (see Supporting Information for
details).
However, here we show that even when that error is avoided, the empirical
Bayesian model-averaging approach of \citet{Hickerson2013} remains biased
toward clustered divergence models, and is predisposed to excluding true
parameter space.
The approach provides another means by which the method can ``escape'' models
with large parameter space, and the method's bias toward smaller models
remains.
Importantly, this bias can manifest by preferring narrow, empirically informed
priors that exclude true parameter space.

% We discuss errors in this approach that render some of their results invalid
% and leave the remaining results difficult to interpret.
% Furthermore, we follow the recommendations of \citet{Oaks2012} and present
% simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
% approach.

% \cwlnote{}{This part seems important, but not related to the error in units
% discussed above}
% Another important characteristic of the approach used by \citet{Hickerson2013}
% that makes their results difficult to interpret is their use of narrow,
% empirically guided uniform priors in an approximate-Bayesian model-choice
% framework.
% We discuss the risks associated with this approach in the next section, and
% show how the results of \citet{Hickerson2013} likely exclude true values of the
% model's parameters.

% In addition to this error, we were not able to reproduce the results of
% \citet{Hickerson2013}.
% We followed their methods, generating $5\e6$ prior samples for each of the
% eight models in their Table 1.
% We retained the 10,000 samples from each model with the smallest Euclidean
% distance to the observed summary statistics, and subsequently retained 10,000
% samples from the remaining 80,000.

\section*{The potential implications of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected.''
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors to reflect the large amount of uncertainty about the
model's parameters for their study system (see section ``Specifying and
simulating the joint prior'' of \citet{Oaks2012}).
\citet{Oaks2012} further discuss how the use of uniform prior distributions in
\msb for many of the model's parameters requires investigators to select broad
priors to avoid excluding the truth \textit{a priori}, and how these broad
uniform priors place too much density in improbable regions of parameter space.
What \citet{Hickerson2013} mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and the power of \msb under real-world
situations when a large amount of prior information is available. 
In doing so, \citet{Oaks2012} discuss the potential dangers of taking an
empirical Bayesian approach to model choice (see the last paragraph of
``Assessing prior sensitivity of \msb'' in \citet{Oaks2012}), and we expand on
this here by exploring both the theoretical and practical implications of using
empirically informed priors for Bayesian model choice.

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a method of inductive learning in which Bayes' rule is
used to update our beliefs about a model $M$ as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values for model $M$, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta \given M)$ describes our belief that
any given \myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta, M)$ measures our belief that any dataset \alignment{}{}
will be generated by any state \myTheta{} of model $M$.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}, M) = \frac{p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M)}{p(\alignment{i}{} \given M)},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{} \given M) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M) d\myTheta{}
    \label{eq:marginallikelhiood}
\end{equation}
is the marginal likelihood of the model.
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the unknown probability of it landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), whereas under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times, and so we decide to use these data in specifying a
beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin $N=10$ times, $y=3$ of which land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The maximum a posteriori (MAP) estimate of the probability of heads is 0.429,
and following Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of
our models of interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, and following
Equation~\ref{eq:bayesmodelchoice}, we can calculate the posterior
probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the correct posterior probability of Model 1 given our prior information
and data.

To give the data more weight relative to the prior, we could use it twice, and
calculate an empirical Bayes estimate using a prior of $beta(13,17)$.
This results in a distribution of $beta(16, 24)$ (Figure~\ref{figCoinFlip}),
with a MAP estimate of 0.395, and $p(M_1 \given y=3, N=10) = 0.10$.
The estimated posterior distribution of the parameter, and resulting MAP
estimate, is similar whether or not an empirically informed prior is used.
However, the posterior probability of Model 1 is very sensitive to the
empirical prior, decreasing by 56\%.
By using the empirically informed prior, we ignored prior uncertainty, leading
to an underestimate of our posterior uncertainty (Figure~\ref{figCoinFlip}).
While this did not greatly affect our estimate of \myTheta{}, it did mislead us
toward overconfidence in Model 2.
% Our mode estimate of \myTheta{} under the empirical prior might be closer
% to the true value than our posterior mode.
% Let us assume the truth of the matter is that the coin under study has a broad
% flat edge, and as a result lands on its edge at a certain frequency.
% Hence, both of our models are incorrect (i.e., the outcomes of flipping the
% coin are not binomially distributed).

% Let us say that principal investigator Mary and her new postdoc Will are
% interested in the hypothesis that the mass of George Washington's periwig
% renders the quarter dollar of the United States unfair.
% That is to say their null hypothesis is that the probability of a US
% quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
% They can certainly evaluate this hypothesis, they can have undergraduate
% worker, Joe, flip the coin for them while they tabulate the results.
% But being Bayesians, before they call Joe into the lab, they agree on a
% prior probability to place on the set of all possible probabilities that
% the quarter will land heads when it is flipped.
% Given that neither of them have a quarter, and their prior knowledge that Joe
% moonlights as a magician, and is notorious for performing coin and card tricks
% in the lab, they suspect there is a good chance that the quarter Joe uses will
% be either two-headed or two-tailed.
% So, knowing that the beta distribution is the conjugate prior for a binomial
% likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
% (Figure~\ref{figCoinFlip}).

@@

% %CWL:
% %I like the example, but it may be too cute. It is also too long. I think a
% %contrived example is good, but if there could be an example that is more
% %relevant to model choice and comparison of inaccurate posterior distributions,
% %I think that would be better. This is an example of empirical Bayes, but not
% %the potential problem with the use in msbayes. Unless I am interpreting wrong.
% %I would be careful about making it to cute as well. You may intend to make it
% %easy to understand for a general audience, but it can also seem like talking
% %down to Hickerson et al, who we are responding to. It just depends on how you
% %read it.
% This can be demonstrated with a simple, albeit contrived, example.
% Let us say that principal investigator Mary and her new postdoc Will are
% interested in the hypothesis that the mass of George Washington's periwig
% renders the quarter dollar of the United States unfair.
% That is to say their null hypothesis is that the probability of a US
% quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
% They can certainly evaluate this hypothesis, they can have undergraduate
% worker, Joe, flip the coin for them while they tabulate the results.
% But being Bayesians, before they call Joe into the lab, they agree on a
% prior probability to place on the set of all possible probabilities that
% the quarter will land heads when it is flipped.
% Given that neither of them have a quarter, and their prior knowledge that Joe
% moonlights as a magician, and is notorious for performing coin and card tricks
% in the lab, they suspect there is a good chance that the quarter Joe uses will
% be either two-headed or two-tailed.
% So, knowing that the beta distribution is the conjugate prior for a binomial
% likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
% (Figure~\ref{figCoinFlip}).

\subsection*{Practical concerns about empirically informed uniform priors for
    Bayesian model choice}
% \cwlnote{}{Should this be part of the empirical Bayes section, or something
%     else?}

% \cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes
%     approaches for model choice when using uniform priors can exclude the
%     $truth$ from the prior, which is a violation of Bayes theorem" or something
%     like that. Picking apart what they calculated and we calculated seems like
%     too much detail. I would try to simplify how this is being presented. This
%     can lead into how the use of more appropriate prior distributions should be
%     used.}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors for a method
that has already been shown to be biased toward models with less parameter
space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
many of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, the results of \citet{Hickerson2013} indicate that integration over
parameter space with low likelihood is biasing the method toward models with
smaller parameter space, and as a consequence is biasing the method toward
models that exclude the truth (i.e., toward estimating model-averaged
posteriors dominated by models that exclude true values of parameters of the
model).

%CWL:This should be in the section on model-averaging, not empirical Bayes
%limitations
We explored the propensity of the empirically informed model-averaging approach
of \citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a marginal posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

>>>>

\msb \citep{Huang2011} uses approximate Bayesian computation (ABC) to estimate
the distribution of divergence times among co-distributed pairs of taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
A full description of the model is given in \citet{Oaks2012}.
Frequently, the exact values of the divergence times are hard 
to determine because researchers typically lack precise knowledge 
of the rate at which substitutions occur.
The exact divergence time is therefore often viewed as a nuisance parameter,
and researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence-time parameters can lead to
       support models with few divergence events shared across taxa. Thus, the
       primary inference enabled by the approach is very sensitive to the
       priors on divergence times.
\end{itemize}

This is not surprising given the rich statistical literature that shows that
model marginal likelihoods are quite sensitive to the priors used in Bayesian
model selection
\citep[e.g.,][]{Jeffreys1935,Lindley1957}.
Accordingly, \citet{Oaks2012} suggest the primary cause of spurious support
for models with few divergence parameters is the greater marginal likelihoods
of these models under vague uniform priors, relative to more parameter-rich
models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density imposed by the uniformly distributed prior on divergence times.
Note, this is a statistical issue, extrinsic to \msb, and does not question the
soundness of the numerical approximation machinery of \msb.

\citet{Hickerson2013} suggest the bias is the result of a numerical issue
intrinsic to \msb, concluding the method's rejection algorithm is inefficient
and will be biased toward models with fewer divergence-time parameters, because
the parameter space of these models are more densely sampled relative to models
with more divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results here of analyses that, when combined with the results
of \citet{Oaks2012}, strongly suggest that \msb prefers models with few
divergence-time parameters, because they have greater likelihoods when
averaged over broad uniform priors on divergences times.

\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times and other nuisance parameters could increase the marginal
likelihoods of models with more divergence-time parameters and thus reduce
spurious support for models of temporally clustered divergences.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed uniform priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for a model-choice method that is highly sensitive to priors.

In this paper, we discuss the potential theoretical and practical
considerations of using empirically informed priors for Bayesian model choice.
Furthermore, we evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
Here, we avoid this error, but still find their approach to be biased toward
clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
Our results, when combined with those of \citet{Oaks2012}, suggest that it is
difficult to choose a uniformly distributed prior on divergence times that is
broad enough to confidently contain the true values of parameters while being
narrow enough to avoid spurious support of models with less parameter space.
However, recent work shows more flexible probability distributions without a
hard upper bound (e.g., gamma) can accommodate prior uncertainty in divergence
times without inhibiting the marginal likelihoods of models with more
divergence-time parameters, and as a result, increase the method's power to
detect temporal variation in divergences
\citet{Oaks2014dpp}.

\section*{The potential implications of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} for divergence-time parameters as ``poorly selected.''
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their prior to reflect the large amount of uncertainty about the
timing of divergences across all 22 of the taxa in their study (see section
``Specifying and simulating the joint prior'' of \citet{Oaks2012}).
\citet{Oaks2012} further discuss how the use of uniform prior distributions in
\msb for many of the model's parameters requires investigators to select broad
priors to avoid excluding the truth \textit{a priori}, resulting in too much
density in improbable regions of parameter space.

\citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
data to inform their prior on divergence times (i.e., an empirical Bayesian
approach).
However, \citet{Oaks2012} did use empirically informed priors to mimic
empirical situations in which a large amount of prior information is available;
they did so to assess the prior sensitivity of the method and to determine if
uniform priors in such situations are narrow enough to avoid spurious support
of models with few divergence-time parameters.
The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
highly sensitive to the prior on divergence times.
Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
divergences under the empirically informed priors.

The main argument of \citet{Hickerson2013} is that the priors used by
\citet{Oaks2012} were not informative enough.
They suggest a very narrow, highly informed uniform prior on divergence times
is necessary to avoid the method's preference for models with few
divergence-time parameters.
Such an empirical Bayesian approach to model selection raises some theoretical
and practical concerns, some of which were discussed by \citet{Oaks2012} (see
the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}); we expand on this here.

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a method of inductive learning in which Bayes' rule is
used to update our beliefs about a model $M$ as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values for model $M$, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta \given M)$ describes our belief that
any given \myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta, M)$ measures our belief that any dataset \alignment{}{}
will be generated by any state \myTheta{} of model $M$.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}, M) = \frac{p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M)}{p(\alignment{i}{} \given M)},
    \label{eq:bayesrule}
\end{equation}
as a measure of our beliefs after seeing the new information, where
\begin{equation}
    p(\alignment{i}{} \given M) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{}, M)p(\myTheta{} \given M) d\myTheta{}
    \label{eq:marginallikelhiood}
\end{equation}
is the marginal likelihood of the model.
\end{linenomath}

@@

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the unknown probability of it landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), whereas under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times each, and so we decide to use these data in specifying
a beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin of interest $N=10$ times, $y=3$ of which
land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The maximum a posteriori (MAP) estimate of the probability of heads is 0.429,
and following Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of
our models of interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, we can calculate the
posterior probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the correct posterior probability of Model 1 given our prior
and data.

To give the data more weight relative to the prior, we could use it twice, and
calculate an empirical Bayes estimate using a prior of $beta(13,17)$.  This
results in a ``posterior'' distribution of $beta(16, 24)$
(Figure~\ref{figCoinFlip}), with a MAP estimate of 0.395, and $p(M_1 \given
y=3, N=10) = 0.10$.
The estimated posterior distribution of the parameter, and resulting MAP
estimate, is similar whether or not an empirically informed prior is used.
However, the posterior probability of Model 1 is very sensitive to the
empirical prior, decreasing by 56\%.
By using the empirically informed prior, we ignored prior uncertainty, leading
to an underestimate of our posterior uncertainty (Figure~\ref{figCoinFlip}).
While this did not greatly affect our estimate of \myTheta{}, it misled us
to be overconfident in Model 2.
% Our mode estimate of \myTheta{} under the empirical prior might be closer
% to the true value than our posterior mode.
% Let us assume the truth of the matter is that the coin under study has a broad
% flat edge, and as a result lands on its edge at a certain frequency.
% Hence, both of our models are incorrect (i.e., the outcomes of flipping the
% coin are not binomially distributed).

% This can be demonstrated with a simple, albeit contrived, example.
% Let us say that principal investigator Mary and her new postdoc Will are
% interested in the hypothesis that the mass of George Washington's periwig
% renders the quarter dollar of the United States unfair.
% That is to say their null hypothesis is that the probability of a US
% quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
% They can certainly evaluate this hypothesis, they can have undergraduate
% worker, Joe, flip the coin for them while they tabulate the results.
% But being Bayesians, before they call Joe into the lab, they agree on a
% prior probability to place on the set of all possible probabilities that
% the quarter will land heads when it is flipped.
% Given that neither of them have a quarter, and their prior knowledge that Joe
% moonlights as a magician, and is notorious for performing coin and card tricks
% in the lab, they suspect there is a good chance that the quarter Joe uses will
% be either two-headed or two-tailed.
% So, knowing that the beta distribution is the conjugate prior for a binomial
% likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
% (Figure~\ref{figCoinFlip}).

@@

\subsection*{Practical concerns about empirically informed uniform priors for
    Bayesian model choice}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors for a method
that has already been shown to be biased toward models with less parameter
space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
some of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).

The strong preference for the questionable priors on divergence times (their
$M_1$ and $M_2$) in the model-averaged results of \citet{Hickerson2013} suggest
their approach is biased toward models with less parameter space, and as a
consequence, is biased toward estimating model-averaged posteriors dominated by
models that exclude true values of parameters of the model.
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging
approach of \citet{Hickerson2013}, but set one of the prior models with a
uniform prior on divergence times that is unrealistically narrow, and almost
certainly excludes most, if not all, of the true divergence times of the 22
taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

\subsubsection*{Re-analyses of the Philippines dataset using empirical Bayesian
model averaging}

For our re-analyses of the Philippines dataset we followed the model-averaging
approach of \citet{Hickerson2013}, but with a reduced set of prior models to
avoid their error of mixing units of time (see SI for details).
We used five prior models, all of which had priors on population sizes of
$\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim
U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these models had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
We simulated $1\e6$ random samples from each of the models for a total of
$5\e6$ prior samples.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
From the remaining 50,000 samples, we then retained the 10,000 samples with the
smallest Euclidean distance from the observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
We then repeated this analysis twice, replacing the $M_1$ model with
$M_{1A}$ and $M_{1B}$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of at least
some of the 22 taxa, we are nearly certain that these narrower priors are
incorrect and exclude most, if not all, of the divergence times of the
Philippine taxa.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the method's support of models with less parameter space.
Rather, the method strongly prefers the prior model with the narrowest
distribution on divergence times across all three of our analyses, even when
this model is almost certainly incorrect and excludes the true divergence times
of the Philippine taxa (Table~\ref{tabModelChoiceEmpirical}).

However, \citet{Hickerson2013} vetted the priors used in their model-averaging
approach via ``graphical checks,'' in which the summary statistics from 1000
random samples of each prior model are plotted along the first two orthogonal
axes of a principle component analysis (see Figure 1 of \citet{Hickerson2013}).
To determine if such prior predictive analyses would indicate the $M_{1A}$ and
$M_{1B}$ models are problematic, we performed these graphical checks on our
prior models.
Unfortunately, these prior predictive checks provide no warning that these
priors are too narrow (Figure~S\ref{figPCA}).
Rather, the graphs suggest these incorrect priors are ``better fit''
(Figure~S\ref{figPCA}A--C) than the valid priors similar to those used by
\citet{Oaks2012} (Figure~S\ref{figPCA}D--F).

Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret.

\subsubsection*{Simulation-based assessment of Hickerson et al.'s
\citeyear{Hickerson2013} model averaging over empirical priors}

To better quantify the propensity of Hickerson et al.'s
(\citeyear{Hickerson2013}) approach to exclude the truth, we simulated 1000
datasets in which the divergence times for the 22-population pairs are drawn
randomly from an exponential distribution with a mean of 0.5 ($\divt{} \sim
Exp(2)$).
All other parameters were identically distributed as the $M_1$--$M_5$ models
(Table~\ref{tabModelChoiceEmpirical}).
We then repeated the analysis described above using $1\e6$ random samples from
prior models $M_1$, $M_2$, $M_3$, $M_4$, and $M_5$, retaining 1000 posterior
samples for each of the 1000 simulated datasets.
